Investigating the Applications and Limits of Single Asymmetric Particle Light Scattering using Limited Detection Schemes

### 2022-11-14 Manuscript.tex
more updates

Eq.~\eqref{eq:scale} to give $y(\bar{\bf s},\theta_k)$.

@@

and is centred about $y_k(\bar{\bf s})$ Combining all three detection
angles provides us with the conditional probability that, should the
dimer be in orientation $\hat{\bf n}_\alpha$, it would produce a
signal $y(\bar{\bf s})$:

@@

  p(y(\bar{\bf s})|\hat{\bf n}_\alpha)

@@

e^{-(y_{k}(\hat{\bf n}_\alpha)-y_{k}(\bar{\bf s}))^2/2\sigma_k^2}

@@

\subsection{Parameter Optimisation Results}
\label{sec:3.3}

>>>>

Eq.~\eqref{eq:scale} to give $y_1(\bar{\bf s})$, $y_2(\bar{\bf s})$,
and $y_k(\bar{\bf s})$.

@@

and is centred about $y_k(\bar{\bf s})$.
Combining all three detection angles provides us with the conditional
probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):

@@

@@

e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Parameter Optimisation Results}
\label{sec:3.3}
